Automatic Hadith Graphs using Arabic Morphological Analysis

### 2011-10-12 tex/hadith.ijcnlp.tex
support for min, max boundaries statistics, solved issue in max graph statistics

create a comprehensive genealogical graph from all biblical accounts greatly enhances its study,
since readers would be able to better understand a character's genealogical context and life span. Such comprehensive graphs can be tagged
with time durations between a father and his giving birth of his sons as is common in many biblical accounts.

@@

>>>>

Creating a comprehensive genealogical graph from all biblical accounts greatly enhances its study,
since readers would be able to better understand a character's genealogical context and life span. Such comprehensive graphs can be tagged
with time durations between a father and his giving birth of his sons as is common in many biblical accounts.

@@

%TODO:
%\begin{itemize}
%\item segmentation, boundary (recall and precision)
%\item local graph min boundary (metrics)
%\item local graph max boundary (metrics)
%\item global graph(metrics)
%
%\end{itemize}
